The Genetic Algorithm of GMSE

### 2018-05-25 notebook/ms/SI1.Rmd

>>>>

Game theory is the formal study of strategic interactions, and can therefore be applied to modelling stakeholder actions and addressing issues of cooperation and conflict in conservation [@Lee2012; @Kark2015; @Adami2016; @Tilman2016; @Redpath2018]. In game-theoretic models, agents adopt strategies to make decisions that maximise some type of payoff (e.g., utility, biological fitness). Agents are constrained in their decision-making, and realised pay-offs depend on decisions made by other agents. In simple models, it is often useful to assume that agents are perfectly rational decision-makers, then find optimal solutions for pay-off maximisation mathematically. But models that permit even moderately complex decision-making strategies or pay-off structures often include more possible strategies than are mathematically tractable [@Hamblin2013]. In these models, genetic algorithms, which mimic the process of natural selection (mutation, recombination, selection, reproduction), can find adaptive (i.e., practical, but not necessarily optimal) solutions for game strategies [e.g., @Balmann2000; @Tu2000; @Hamblin2013].
